\rule{\textwidth}{4pt}\\[1em] \textbf{From Distribution Forecasts to Vanilla Portfolios: \\[0.2cm] Regularized Payout Approximation in Discrete Space}\\[1em] \rule{\textwidth}{2pt}

### 2025-02-18 latex/article.tex
costs are not problem

where \( \boldsymbol{\theta} = (\lambda, \{\alpha_i\}, \{\beta_j\}) \) represents
the position weights, \( \gamma \) is the regularization parameter, 
\( S_{\min}, S_{\max} \) define the approximation domain, and \( p \) determines
the type of regularization. The L2 norm (\(p=2\)) promotes smoother weight 
distributions, while the L1 norm (\(p=1\)) tends to produce sparse solutions by 
setting some weights exactly to zero, which can be beneficial when portfolio 
simplicity or transaction costs are important considerations.

>>>>

where \( \boldsymbol{\theta} = (\lambda, \{\alpha_i\}, \{\beta_j\}) \) represents
the position weights, \( \gamma \) is the regularization parameter, 
\( S_{\min}, S_{\max} \) define the approximation domain, and \( p \) determines
the type of regularization. The L2 norm (\(p=2\)) promotes smoother weight 
distributions, while the L1 norm (\(p=1\)) tends to produce sparse solutions by 
setting some weights exactly to zero, which can be beneficial when portfolio 
simplicity is important consideration.
